Constructing a universe for the setoid model

### 2021-01-21 paper.tex
Fix incorrect description of types over I.

Induction-recursion is arguably a nice and natural way to define internal
universes in type theory, however it is not always strictly required.
%
We can translate basic instances of induction-recursion into inductive families
using the equivalence of $I$-indexed families of types and types over $I$
(that is, $\mType_i \to I$) \cite{malatasta13smallir}. % TODO: fix wrong formula

>>>>

Induction-recursion is arguably a nice and natural way to define internal
universes in type theory, however it is not always strictly required.
%
We can translate basic instances of induction-recursion into inductive families
using the equivalence of $I$-indexed families of types and types over $I$
(that is, $A : \mType$ with $A \to I$) \cite{malatasta13smallir}.
